\documentclass[11pt,a4paper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{amsmath}
\usepackage{amssymb}

\setmainlanguage{english}
\setotherlanguage{hebrew}
\newfontfamily\hebrewfont{DejaVu Sans}[Script=Hebrew]

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\pagestyle{fancy}
\fancyhf{}
\rhead{Knesset Protocol Journal Project}
\lhead{Step 8 --- Retrieve-then-Verify}
\rfoot{Page \thepage}
\lfoot{Tomer Morad, Or Israeli, Yoel Marko --- July 2026}

\titleformat{\section}{\large\bfseries}{\thesection.}{0.6em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.6em}{}

\begin{document}

\begin{center}
  {\LARGE \textbf{Retrieve-then-Verify: an LLM Verifier for Streaming Linking}}\\[0.3em]
  {\large Step 8 --- Task 2b, CLAUDE.md Milestone 3b}\\[0.6em]
  {\normalsize Tomer Morad \quad Or Israeli \quad Yoel Marko}\\
  {\normalsize July 2026}
\end{center}

\vspace{0.5em}

\section{Objective}

Step 7 showed that no fixed cosine threshold on e5\_k1 similarity can separate rare true
repeats from the flood of similar-sounding unrelated topics at gold-segmentation granularity
(best-F1 streaming precision $\approx$8\%). This step tests the project brief's proposed fix:
use similarity only to \emph{retrieve} a candidate shortlist, then have an \textbf{LLM verifier}
read the actual text and decide same/related/new, rather than trusting a vector-distance cutoff.
\textbf{Status: paused below baseline, not dead-ended} --- every configuration tried is
documented here, including several that made things worse, because the negative results are as
informative as the positive ones for scoping future work.

\section{Method}

\textbf{Retrieval side.} An oracle-growth journal (new entry created on each topic's true first
occurrence) ranks existing entries by e5\_k1 cosine similarity for all 36 gold repeat events.

\textbf{Verifier side.} 522 streaming-decision queries, each with the new segment's text and its
top-10 retrieved candidates (100-word content-only snippets, deliberately excluding the gold
topic label to prevent string-matching the answer). Three local HF chat models compared:
\texttt{dicta-il/dictalm2.0-instruct}, \texttt{Qwen2.5-7B-Instruct}, \texttt{Qwen2.5-3B-Instruct}.
The model picks the best-matching candidate rank and a 0--100 confidence score, swept as a
threshold exactly like Step 7's cosine curve for direct comparability.

\section{Results}

\subsection{Retrieval recall@K --- never the bottleneck}
\begin{center}
\begin{tabular}{lrrrrr}
\toprule
$K$ & 1 & 2 & 3 & 5 & 10 \\
\midrule
Recall & 0.694 & 0.778 & 0.917 & 0.944 & \textbf{1.000} \\
\bottomrule
\end{tabular}
\end{center}
All 36/36 gold repeats are retrievable in the top 10. Three embedding/lexical fixes for the 69\%
recall@1 gap (regex boilerplate stripping, TF-IDF rerank, ministry-name gating) were each tried
and ruled out with evidence (ceiling $\approx$+1/36 in all three cases) --- the corpus's
recurring ``year-end budget surplus'' sessions share so much administrative vocabulary across
\emph{different} ministries that lexical tricks cannot cleanly separate them; one case needs
genuine reading comprehension (same ministry, same section, different specific matter). This
motivated committing to an LLM verifier rather than continuing to chase retrieval fixes.

\subsection{Verifier comparison --- 6 real bugs fixed en route}
Getting to a working, comparable verifier required: (1) merging system+user roles for
DictaLM's chat template, (2) stopping models from literally continuing the (likely memorized)
real transcript text past the prompt cutoff, (3--4) anchoring the exact JSON schema with a
worked example without \texttt{no\_repeat\_ngram\_size} banning the model from legitimately
repeating that schema's tokens, (5) discovering a fixed same/new decision was miscalibrated
completely differently per model, fixed by (6) switching to a swept 0--100 confidence score.

\begin{center}
\begin{tabular}{lrrrr}
\toprule
\textbf{Model} & \textbf{Best F1} & \textbf{Precision} & \textbf{Recall} & \textbf{$\theta$} \\
\midrule
dictalm2 & 0.086 & 4.5\% & 92.0\% & 0 \\
\textbf{qwen3b} & \textbf{0.111} & 6.0\% & 70.4\% & 65 \\
qwen7b & 0.077 & 4.0\% & 95.0\% & 15 \\
\midrule
\textbf{Baseline (e5\_k1 threshold, Step 7)} & \textbf{0.125} & 7.7\% & 33.3\% & --- \\
\bottomrule
\end{tabular}
\end{center}
Recall is excellent across all three models (70--95\%, vs.\ baseline's 33\%) --- they genuinely
find almost every true recurrence. \textbf{Precision is the isolated bottleneck.}

\subsection{Four precision-calibration experiments}
\begin{center}
\small
\begin{tabular}{p{5.2cm}rrr}
\toprule
\textbf{Experiment} & \textbf{qwen3b F1} & \textbf{qwen7b F1} & \textbf{dictalm2 F1} \\
\midrule
baseline & \textbf{0.111} & 0.077 & 0.086 \\
Ensemble (majority vote, no new LLM calls) & \multicolumn{3}{l}{0.109 --- ties qwen3b, doesn't beat it} \\
+more few-shot examples (2$\to$4) & 0.104 $\downarrow$ & 0.070 $\downarrow$ & 0.057 $\downarrow$ \\
+two-score schema (topical vs.\ specific) & 0.102 $\downarrow$ & \textbf{0.085} $\uparrow$ & \textbf{0.096} $\uparrow$ \\
+longer snippets (100$\to$400 words) & 0.068 $\downarrow\downarrow$ & 0.055 $\downarrow\downarrow$ & 0.000 (broke) \\
\bottomrule
\end{tabular}
\end{center}

\textbf{None beat the baseline.} Ensemble majority-voting successfully filters dictalm2/qwen7b's
excess false positives (precision rises to 5.9\% vs.\ their 4.0--4.5\%) but cannot exceed the
best individual model once it's one of the three votes. Longer snippets actively hurt every
model and broke dictalm2 outright (its old document-continuation failure mode resurfaces at
longer context). More few-shot examples also hurt across the board. The two-score schema is the
one genuinely interesting result: it helped the two \emph{more miscalibrated} models
(dictalm2, qwen7b) but slightly hurt qwen3b, which was already well-calibrated.

\section{What Needs Improvement}

\begin{enumerate}[leftmargin=1.4em]
  \item \textbf{The precision ceiling is real and evidenced, not a quick prompt-engineering
        fix.} Four different calibration ideas were tried; none closed the gap to baseline.
  \item \textbf{Two separate scores helped the weaker models} --- worth exploring further with
        the two-score schema \emph{and} extended few-shot together (not yet combined), or with
        a larger model.
  \item \textbf{Whether the 100-word snippet cap is fundamentally too little context}, or
        whether longer context is inherently harmful for this classification-style task
        (unlike Step 9's free-text generation, where more context per candidate was never
        tried) remains genuinely open.
  \item \textbf{``Related'' predictions are unused.} The current schema only distinguishes
        LINK vs.\ NEW for scoring, since gold has no 3-way label. Whether ``related'' is usable
        for Task 3 (log writing) input is still open.
  \item \textbf{Recommendation for now}: keep method (a), the similarity-threshold baseline,
        as the production linking method (decision made 2026-07-15) --- it remains the best of
        everything tried, including this step's LLM verifier.
\end{enumerate}

\vspace{1.5em}
\hrule
\vspace{0.4em}
\raggedright
{\small
\textbf{Artifacts (this step):} \newline
\texttt{outputs/shortlist\_recall.json}, \texttt{outputs/verifier\_queries.json}, \newline
\texttt{outputs/verifier\_predictions\_*.json} (14 configs), \texttt{outputs/verifier\_eval\_summary.json} \newline
\textbf{Code:} \texttt{code/build\_verifier\_inputs.py}, \texttt{code/run\_verifier.py},
\texttt{code/eval\_verifier.py}, \texttt{code/ensemble\_verifier.py}, \newline
\texttt{code/shortlist\_recall.py}, \texttt{code/rerank\_recall.py},
\texttt{code/ministry\_gate\_recall.py}, \newline \texttt{code/strip\_procedural.py},
\texttt{code/inspect\_misses.py}.
}

\end{document}
