\documentclass[11pt,a4paper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{amsmath}
\usepackage{amssymb}

\setmainlanguage{english}
\setotherlanguage{hebrew}
\newfontfamily\hebrewfont{DejaVu Sans}[Script=Hebrew]

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\pagestyle{fancy}
\fancyhf{}
\rhead{Knesset Protocol Journal Project}
\lhead{Step 9 --- Log Writing}
\rfoot{Page \thepage}
\lfoot{Tomer Morad, Or Israeli, Yoel Marko --- July 2026}

\titleformat{\section}{\large\bfseries}{\thesection.}{0.6em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.6em}{}

\begin{document}

\begin{center}
  {\LARGE \textbf{Context-Conditioned Log Writing}}\\[0.3em]
  {\large Step 9 --- Task 3: incremental, RAG-style journal summarization}\\[0.6em]
  {\normalsize Tomer Morad \quad Or Israeli \quad Yoel Marko}\\
  {\normalsize July 2026}
\end{center}

\vspace{0.5em}

\section{Objective}

Task 3 (previously entirely unstarted): given the existing journal entry for a legislative
matter and a new protocol segment about that same matter, generate \emph{only} the incremental
contribution --- new developments, decisions, status changes --- not a full re-summary.
Faithfulness is defined as chain-relative: judged against the summary chain built so far, not
by re-deriving ground truth from every prior session's raw transcript.

\section{Method}

\textbf{Deliberately built on Step 7's gold chains}, not method (a)'s predicted linking output:
method (a) is only 7.7\% precision at best-F1, so using its predicted chains here would conflate
``is the summarizer bad'' with ``is the upstream linking bad.'' Same isolation precedent as
Step 7 separating Task 1 from Task 2.

For each of the 22 gold-recurring chains (36 total incremental-update instances): generate an
opening entry from the first occurrence alone, then for each subsequent occurrence, generate an
update given (a) the running journal built from the model's \emph{own} prior generations and
(b) the new occurrence's text (capped at 700 words). Two generators compared:
\texttt{dictalm2.0-instruct} (Hebrew-native) and \texttt{Qwen2.5-7B-Instruct}. Every entry is
then scored by an independent judge (\texttt{Qwen2.5-3B-Instruct}, not used for generation, to
avoid self-preference bias) on two 0--100 axes: \textbf{faithfulness} (grounded in the source
text, no hallucination) and \textbf{novelty} (updates only --- genuinely new content vs.\ just
restating the existing journal).

\section{Results}

\begin{center}
\small
\begin{tabular}{lrrrr}
\toprule
\textbf{Prompt version} & \textbf{dictalm2 F.} & \textbf{dictalm2 N.} & \textbf{qwen7b F.} & \textbf{qwen7b N.} \\
\midrule
\textbf{original (no few-shot)} & \textbf{80.7} & \textbf{18.1} & 63.4 & \textbf{10.1} \\
v2 (real-corpus example) & 71.1 & 15.0 & 63.1 & 8.3 \\
v3 (fictional example) & 53.6 & 5.0 & \textbf{69.2} & 5.3 \\
\bottomrule
\end{tabular}
\\[0.3em]
{\footnotesize F. = mean faithfulness, N. = mean novelty (updates only), both 0--100.}
\end{center}

All three configurations had 0/58 JSON parse errors. \textbf{Faithfulness}: dictalm2 (Hebrew-
native) is consistently more grounded than qwen7b on the original prompt --- the opposite
pattern from Step 8, where dictalm2 struggled with rigid JSON-schema output but this is
free-text generation, playing to its strength.

\textbf{Novelty is the central open problem}, and two attempted fixes made it \emph{worse}, not
better. v2 added a worked BAD-vs-GOOD example built from real corpus content: 13/36 (36\%) of
dictalm2's updates turned out to be \emph{literal verbatim copies} of the worked example's
answer, regardless of the actual input. v3 rebuilt the example with fully fictional content plus
an explicit anti-copying instruction, hypothesizing real-corpus content was the specific
problem --- this made copying \emph{worse} (33/36 = 92\%), traced to an authoring bug (a literal
placeholder left in the fictional example's source-text slot, giving the model nothing to reason
from except the fixed answer). \textbf{More importantly, independent of that bug}: novelty
declined monotonically for \emph{both} models across all three versions, including qwen7b, which
had zero copying issue at all (10.1 $\to$ 8.3 $\to$ 5.3). Few-shot examples for this specific
free-text incremental-diff task cause imitation of the example's \emph{content}, not just its
\emph{style} --- the opposite of Step 8's classification task, where few-shot genuinely helped.

\section{What Needs Improvement}

\begin{enumerate}[leftmargin=1.4em]
  \item \textbf{Recommendation: use the original (zero-few-shot) prompt.} It is best or
        tied-best on every metric for dictalm2, and few-shot didn't meaningfully help qwen7b
        either.
  \item \textbf{Novelty scores are low across the board} (best case 18.1/100) --- even without
        the few-shot regression, genuinely incremental (not recap-laden) log writing is unsolved.
  \item \textbf{Untried next lever}: force a structured ``what changed'' bullet-list output
        instead of free prose, which should be harder to blend a copied/recapped example into
        than a flowing paragraph. Not attempted in this step.
  \item \textbf{No human-written reference summaries exist} for this corpus, so faithfulness/
        novelty are judged by an LLM against the same context the generator saw, not by
        comparison to a gold summary. A small human-annotated reference set (even 5--10 chains)
        would substantially strengthen this evaluation.
  \item \textbf{Built on gold chains, not predicted linking} --- by design, so this step's
        numbers say nothing about end-to-end pipeline quality (linking + log writing together).
        That combined evaluation has not been run.
\end{enumerate}

\vspace{1.5em}
\hrule
\vspace{0.4em}
\raggedright
{\small
\textbf{Artifacts (this step):} \newline
\texttt{outputs/journal\_chains.json}, \texttt{outputs/generated\_logs\_*.json} (6 configs), \newline
\texttt{outputs/faithfulness\_scores\_*.json}, \texttt{outputs/faithfulness\_summary.json} \newline
\textbf{Code:} \texttt{code/build\_journal\_chains.py}, \texttt{code/generate\_logs.py},
\texttt{code/eval\_faithfulness.py}.
}

\end{document}
